Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-27 writing/DraftExposurePaper/DraftExposurePaper.Rmd
loop work

```{r}
test <- data.frame(fips = ike_fips[1:2], station = NA)
#for(fips in ike_fips[1:2]){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        test[fips, "stations"] <- max(ike_weather$daily_weather$prcp_reporting)
} #Still working on it
ike_table <- data.frame(fips = ike_fips, station = NA)
#for(fips in ike_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ , "station"] <- max(ike_weather$daily_weather$prcp_reporting)
} #still working on it
```

>>>>

```{r}
my_fips <- ike_fips[1:3]
my_stations <- NA
test <- expand.grid(my_fips, my_stations)
colnames(test) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        test[test$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} #This works fine (small subset of code below)
ike_table <- expand.grid(ike_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
#for(fips in ike_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)
} #getting error
```
